---
title: "Home"
format: html
editor: visual
---

```{r, echo=FALSE, warning=FALSE}
library('slickR')
```

```{r, echo=FALSE}
library(slickR)

imgs <- c("image04.jpg", "image05.jpg", "image2.jpg", "image01.jpg", "image06.jpg", "image07.jpg", "image03.png", "image08.jpg")

carousel <- slickR(obj = imgs, slideType = "img", width = "90%", height = 400)

carousel + settings(
  autoplay = TRUE,
  autoplaySpeed = 2000,
  infinite = TRUE,
  dots = TRUE,
  arrows = TRUE
)

```

```{=html}
<style>
  .slick-slide img {
    position: relative;
  }

  .caption-overlay {
    position: absolute;
    bottom: 0;
    width: 100%;
    background: rgba(0,0,0,0.4); /* nice transparency */
    color: white;
    padding: 10px;
    text-align: center;
    font-size: 1.1em;

    /* Fade-in stuff */
    opacity: 0;
    transition: opacity 0.4s ease-in-out;
  }

  .slick-active .caption-overlay {
    opacity: 1;
  }

  .slick-slide {
    position: relative;
  }
</style>
```

```{=html}
<script>
  // Wait for the DOM to finish loading
  document.addEventListener("DOMContentLoaded", function () {
    const captions = [
      " ",
      "Acting in boom",
      "First ever presentation at ASM Omaha!",
      "Leading Honors Book Club",
      "More boom!",
      "Presenting at annual INBRE presentation",
      "Gingerbread house competition fun with friends",
      "Move in fun with Abby",
      "Storm game with the Delts"
    ];

    const slides = document.querySelectorAll(".slick-slide");

    slides.forEach((slide, i) => {
      if (!slide.querySelector('.caption-overlay') && i < captions.length) {
        const caption = document.createElement("div");
        caption.className = "caption-overlay";
        caption.innerText = captions[i];
        slide.appendChild(caption);
      }
    });
  });
</script>
```

Hello! I’m **Caleb Rother**, a sophomore at the University of Nebraska at Kearney (UNK) majoring in Molecular Biology with a minor in Media Production.

```{r, echo=FALSE, warning=FALSE}
# Example: Display your latest blog posts or GitHub projects dynamically
library(quarto)
#quarto::quarto_render()
```

I am actively involved on campus through Fraternity and Sorority Life (FSL), the Honors Program, and my undergraduate research. I love making new friends throughout campus, and aim to have a diverse perspective of UNK. I aim to improve the campus, community, and culture of UNK through a variety of projects and initiatives.

<a href="Student.html" class="fancy-button">Read more about my campus projects</a>

I hope to leave UNK with a strong foundation in scientific concepts, especially relating to host-pathogen interactions and immunology. I believe a good scientist should have strong communication skills, not just with other scientists, but also with the general public.

<a href="Research.html" class="fancy-button">Read more about my research</a>

```{=html}
<style>
.fancy-button {
  background: linear-gradient(135deg, #7e57c2, #9575cd);
  color: white;
  padding: 0.6em 1.2em;
  border: none;
  border-radius: 30px;
  text-decoration: none;
  font-weight: 500;
  font-size: 1rem;
  box-shadow: 0 4px 6px rgba(0, 0, 0, 0.1);
  text-shadow: 0 1px 2px rgba(0, 0, 0, 0.2);
  transition: all 0.3s ease-in-out;
  display: inline-block;
  cursor: pointer;
}

.fancy-button:hover {
  background: linear-gradient(135deg, #673ab7, #9575cd);
  box-shadow: 0 8px 16px rgba(103, 58, 183, 0.3);
  transform: translateY(-2px);
}
</style>
<style>
  /* General body styling */
  body {
    font-family: 'Roboto', sans-serif;
    line-height: 1.6;
    color: #333;
    background-color: #f0f4f8;  /* Light greyish background */
  }

  /* Carousel styling */
  .slick-slide img {
    background-color: #f0f4f8;  /* Light greyish background */
    border-radius: 10px;  /* Rounded corners for images */
  }

  /* Style for carousel container */
  .slick-list {
    background-color: #f0f4f8;  /* Same background as body */
    border-radius: 10px;
  }

  /* Add shadow for carousel for a sleek effect */
  .slick-track {
    box-shadow: 0 4px 8px rgba(0, 0, 0, 0.1);
  }

  /* Navigation bar styling */
  .navbar {
    background-color: #673ab7; /* Use a nice blue color or any color that complements your theme */
    color: white;
    padding: 15px;
    border-bottom: 2px solid #333; /* Optional: a border at the bottom for some definition */
  }

  /* Navigation bar links */
  .navbar a {
    color: white;
    text-decoration: none;
    font-size: 1.1em;
    margin-right: 15px;
  }

  .navbar a:hover {
    color: #e1e1e1;  /* A subtle hover effect */
  }

  /* Caption overlay for carousel with improved transparency */
  .caption-overlay {
    position: absolute;
    bottom: 0;
    width: 100%;
    background: rgba(0, 0, 0, 0.4); /* Nice transparency */
    color: white;
    padding: 10px;
    text-align: center;
    font-size: 1.1em;

    /* Fade-in effect */
    opacity: 0;
    transition: opacity 0.4s ease-in-out;
  }

  .slick-active .caption-overlay {
    opacity: 1;
  }

  /* Optional: Change the dots and arrows color for better contrast */
  .slick-prev, .slick-next {
    color: ##673ab7;  /* Blue arrows for consistency */
  }
  /* Navigation bar links */
.navbar a {
    color: white; /* Make the Home button (and others) white */
    text-decoration: none;
    font-size: 1.1em;
    margin-right: 15px;
}

/* Hover effect on navbar links */
.navbar a:hover {
    color: #e1e1e1;  /* A subtle hover effect when hovering over the button */
}


/* Carousel container (slick-list) background */
.slick-list {
  background-color: #f0f4f8;  /* Light greyish background */
  border-radius: 10px;  /* Rounded corners for the carousel container */
  overflow: hidden;  /* Prevents overflow outside the carousel */
}

/* Individual slick-slide background */
.slick-slide {
  background-color: #f0f4f8; /* Light greyish background */
  display: flex;
  justify-content: center;  /* Aligns the image to the center */
  align-items: center;  /* Vertically centers the image */
}

/* Carousel images - ensure full container coverage */
.slick-slide img {
  width: 100%;  /* Image will stretch to fill width */
  height: 100%;  /* Image will stretch to fill height */
  object-fit: cover;  /* Maintain aspect ratio and crop if necessary */
  border-radius: 10px;  /* Rounded corners for images */
}

</style>
```

<footer>

<p>Created by Caleb Rother 2025 \| University of Nebraska at Kearney</p>

</footer>
